plyranges: a grammar for transforming genomics data

### 2018-04-19 paper.Rmd
reworking opportunities --> limitations

## Limitations

A caveat to constructing a compatible interface with `dplyr` is that 
`plyranges` makes extensive use of non-standard evaluation in R
(achieved via the `rlang` package @R-rlang). Simply, this
means that computations are performed and evaluated in the context of the 
GRanges objects, which emphasises the interactive nature of the interface.
This has the disadvantage that programming with `plyranges` becomes more difficult 
because a user needs to know about non-standard evaluation and user defined
functions can be difficult to debug.

>>>>

## Opportunities

A caveat to constructing a compatible interface with `dplyr` is that 
`plyranges` makes extensive use of non-standard evaluation in R
(achieved via the `rlang` package @R-rlang). Simply, this
means that computations are performed and evaluated in the context of the 
GRanges objects; emphasising the interactive nature of our API.
Consequently, when programming with `plyranges` a user needs to be aware of
how non-standard evaluation in R works and how to adapt their code 
accordingly. However, with the rise of R packages like `rlang` this process
is becoming less difficult.

While GRanges are an intuitive representation for data measured on genomic regions,
more flexible data structures are required to represent data from multiple sample
experiments. The Bionconductor class SummarizedExperiment is the canonical 
data structure for representing data for combining multiomic measurements 
from multiple samples. The grammar and design of the `plryanges` DSL can be
naturally extended to the SummarizedExperiment.
